Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-05-19 causal-bandit/nips_2016/introduction.tex
updates

A well-studied class of bandit problems with side information are ``contextual bandits''~\cite{Langford2008,Agarwal2014}. Our framework bears a superficial similarity to contextual bandit problems since the extra observations on non-intervened variables might be viewed as context for selecting an intervention. 
However, a crucial difference is that in our model the extra observations are only revealed \emph{after} selecting an intervention and hence cannot be used as context. % We discuss the relationship between causal and contextual bandits further in \S\ref{sec:defs} and leave their combination as future work.

There have been several proposals for bandit problems where extra feedback is received after an action is taken.
Most recently, \citet{Alon2015}, \citet{Kocak2014} and \citet{wu2015online} have considered very general models related to partial monitoring games~\citep{Bartok2014} where rewards on unplayed actions are revealed according to a feedback graph. As we discuss in \S\ref{sec:discussion}, the problem they consider shares some similarity with ours however their results are for cumulative regret and thus cannot be used to guarantee low simple regret~\citep{Bubeck2009a}.
% Even in the case of cumulative regret we show that an application of their results to the parallel bandit problem with $N$ variables yields a $\bigo{\sqrt{NT}}$ bound.
\citet{Yu2009} consider bandit problems where a learner chooses an arm to play as well as set of arms to observe rewards for in a stochastic setting where the reward distributions can change infrequently and the aim is to minimize cumulative regret.
They use extra observations to detect changes whereas we assume fixed reward distributions and use extra observations to improve arm selection.
\citet{Avner2012} analyse bandit problems where the choice of arm to pull and arm to receive feedback on are decoupled. 
The main difference from our present work is our focus on simple regret and exploitation of the more complex information related rewards via the causal graph.
To the best of our knowledge, our paper is the first to analyse simple regret in bandit problems with extra post-action feedback.

>>>>

A well-studied class of bandit problems with side information are ``contextual bandits''~\cite{Langford2008,Agarwal2014}. Our framework bears a superficial similarity to contextual bandit problems since the extra observations on non-intervened variables might be viewed as context for selecting an intervention. 
However, a crucial difference is that in our model the extra observations are only revealed \emph{after} selecting an intervention and hence cannot be used as context.

There have been several proposals for bandit problems where extra feedback is received after an action is taken.
Most recently, \citet{Alon2015}, \citet{Kocak2014} have considered very general models related to partial monitoring games~\citep{Bartok2014} where rewards on unplayed actions are revealed according to a feedback graph. As we discuss in \S\ref{sec:discussion}, the problem they consider shares some similarity with ours however their results are for cumulative regret and thus cannot be used to guarantee low simple regret~\citep{Bubeck2009a}. Even without this difference, none
of these algorithms could be applied to our general setting without modification and even in the parallel bandit setting their regret guarantees would not be optimal.
The partial monitoring approach taken by \cite{wu2015online}
could be applied in principle (up to modifications for the simple regret) to the parallel bandit, but the resulting strategy would need to know the likelihood 
of each factor in advance, while our strategy learns this online.
\citet{Yu2009} consider bandit problems where a learner chooses an arm to play as well as set of arms to observe rewards for in a stochastic setting where the reward distributions can change infrequently and the aim is to minimize cumulative regret.
They use extra observations to detect changes whereas we assume fixed reward distributions and use extra observations to improve arm selection. 
\citet{Avner2012} analyse bandit problems where the choice of arm to pull and arm to receive feedback on are decoupled. 
The main difference from our present work is our focus on simple regret and exploitation of the more complex information related rewards via the causal graph.
To the best of our knowledge, our paper is the first to analyse simple regret in bandit problems with extra post-action feedback.
